---
title: "Homework 08"
author: "Maddy Degelsmith"
date: "3/31/2021"
output: html_document
---

# Ranavirus Hypothesis
Tadpoles with heterozygosity will have lower viral loads than those with homozygosity


### Original Sample size: **80** (40 homozygous & 40 heterozygous tadpoles)
### Standard Deviation: **500**

  * I used 500 because viral load can vary A LOT 
  
### homozygous mean: **10000**

 * I used this number since homozygous tadpoles would be more likely to die and would have a larger viral load
  
### heterozygous mean: **3000**

  * I used this number because a lower viral load means the tadpole would be less likely to die


```{r}
# ---------------------------
# homework 8 script
# 31 Mar 21
# MJD
# ---------------------------
# homozygous tadpoles - higher viral load
# heterozygous tadpoles - lower viral load
library(tidyr)
library(ggplot2)

sampleSize <- 1:40

# random normal data for homzygous
homozygous <- rnorm(n=sampleSize, mean = 10000, sd =500)
homozygous 

# random normal data for heterozygous
heterozygous <- rnorm(n=sampleSize, mean = 3000, sd = 500)


df <- data.frame(homozygous, heterozygous)
df

# making a data frame
df2 <- gather(df,group,virus)
df2

# statistical analysis
anova <- aov(virus~group, data=df2)
summary(anova)

p1 <- ggplot(data=df2, mapping=aes(x=group, y=virus, fill=group)) +
               geom_boxplot() 
             p1


```

### in order for my p-value to be insignificant, I had to change the difference in viral load mean to less than 100 between homozygous (4000) & heteroxygous (3900)

```{r}

library(tidyr)
library(ggplot2)

sampleSize <- 1:40

# random normal data for homzygous
homozygous <- rnorm(n=sampleSize, mean = 4000, sd =500)
homozygous 

# random normal data for heterozygous
heterozygous <- rnorm(n=sampleSize, mean = 3900, sd = 500)


df <- data.frame(homozygous, heterozygous)
df

# making a data frame
df2 <- gather(df,group,virus)
df2

# statistical analysis
anova <- aov(virus~group, data=df2)
summary(anova)


p1 <- ggplot(data=df2, mapping=aes(x=group, y=virus, fill=group)) +
               geom_boxplot() 
             p1

```

### With the original means, any sample size led to significant results since the means were so different
```{r}
library(tidyr)
library(ggplot2)

sampleSize <- 1:2

# random normal data for homzygous
homozygous <- rnorm(n=sampleSize, mean = 10000, sd =500)
homozygous 

# random normal data for heterozygous
heterozygous <- rnorm(n=sampleSize, mean = 3000, sd = 500)


df <- data.frame(homozygous, heterozygous)
df

# making a data frame
df2 <- gather(df,group,virus)
df2

# statistical analysis
anova <- aov(virus~group, data=df2)
summary(anova)


p1 <- ggplot(data=df2, mapping=aes(x=group, y=virus, fill=group)) +
               geom_boxplot() 
             p1

```


